Mapping plant-pollinator interactions across Europe

### 2024-02-07 Manuscript/Ms.qmd
Good day, aiming for Global Ecol and Biogeography. And probably lacking 2 graphs.

@@

@@

@@

Create definitions here based on Corine

1)Pastures: Any type of low growing plant community that is highly influenced by human disturbance. For instance, agriculture, mowing, moderate to high grazing or urban environment. Note that this category also includes old pastures with regrowth of woody vegetation.

2)Agricultural margings: Sides of crops that can include any type of vegetation from low growing plants to trees.

3)Agricultural land: Includes any type of crop and any type of vegetation growing within them.

4)Semi-natural grassland: Low growing plant community with relatively low disturbances but under low pressure such as seasonal mowing or extensive grazing.

5)Ruderal vegetation: Plants growing on highly disturbed sites such as road sides or mineral extraction sites.

6)Sclerophyllous vegetation: Any type of system with a dominant shrub community adapted to drought. Typical of the Mediterranean region. Note, that we have include in this category also woodlands (open coniferous forest) where the shrub community was the main focus of the study.

7) Green urban areas: Parks, private gardens or small pastures within an  urban setting. For simplicity, we have also included botanical gardens.

8) Forest/woodland understory: Any plant community sampled under a wooded group of plants 
The forest could be embedded in an agricultural setting or in a fully natural scenario. We have included here agro-forestry areas, open forest to dense forest but try to exclude forest that contains typical sclerophyllous vegetation.

9) Riparian vegetation: Plant communities growing on river margins.

10): Low growing plant communities with little or none human disturbance. Often located in high elevation areas within Europe.

11) Beaches, dunes, sands: Plant communities growing on sandy soil.

12) Moors and heathland: Low growing woody vegetation characteristic from low fertile soils near the coast or in alpine areas.

>>>>

## Data structure?

TABLE? Describe cols?

@@

```{r echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, out.width="95%", fig.cap= "\\textbf{Figure 3}. a) Phylogenetic tree of plant families in the Safenet database, showing the number of species per family in logarithmic scale (blue circles) and the total number of interactions recorded per family (gray bars). b) Comparison of the top 50 families with the highest number of species in the SafeNet database against the total number of species recorded for those families at the European level. Species counts are displayed in logarithmic scale for better visualization.", fig.width=8, fig.height=8}

library(ggplot2)
library(ggtree)
library(ggnewscale)
library(ggtreeExtra)
library(cowplot)

#Save data to plot it in markdown file
c = readRDS("../Data/Working_files/Figures/data_figure3b.rds")
tree_family_interactions = readRDS("../Data/Working_files/Figures/data_figure3a1.rds")
plant_fam_interactions = readRDS("../Data/Working_files/Figures/data_figure3a2.rds")

# The circular layout tree
p = ggtree(tree_family_interactions, 
    layout="fan", size=0.1, open.angle=5, alpha=0.5)+ 
geom_tippoint(aes(size= Family_species), colour='cyan4') +
geom_tiplab(linetype='dashed', linesize=.05, 
    size=1.75, color= "black", offset = -45, fontface="bold") +
labs("log(Species)")+
scale_size(name = "log(Species #)") +
ggtitle("a)") +
theme(plot.title = element_text(vjust = -31, hjust = 0.12, size = 14),
      legend.position = "bottom")

#Create barplot around circular tree
p1 = p + 
new_scale_fill() +
geom_fruit(data=plant_fam_interactions, geom=geom_bar,
   mapping=aes(y=Plant_family1, x=Family_interactions1),
   pwidth=0.38, 
   orientation="y", 
   stat="identity", 
   color = "black") +
theme(legend.margin=margin(0,0,0,0),
   legend.box.margin=margin(-50,-50,-50,-50),
   plot.margin = margin(-15, -15, -10, -10, "pt")) +
scale_size(name = "log(species number)", range=c(0,4))

p2 = ggplot() + 
geom_col(data = c, 
  aes(x = reorder(Family_names, Spp_per_family), 
  y = log(Spp_per_family), fill = Group), position=position_dodge(0.1),width=1) +
xlab(NULL) +
ylab("log(species number)") +
theme_bw() +
theme(axis.text.y = element_text(size = 5, face = "bold", color = "black"),
      panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
coord_flip(expand = F) +
scale_fill_manual(name="", values = c("black", "cyan4")) +
  theme(plot.margin = margin(-10, 0, -10, -10, "pt")) +
ggtitle("b)")+
theme(legend.margin=margin(0,0,0,0),
   legend.box.margin=margin(-10,-10,-10,-10)) +
  theme(legend.key.size = unit(0.3, 'cm'),
        legend.position = "bottom",
        plot.title = element_text(size=14))

p2_1 = plot_grid(NULL,p2,NULL, ncol = 1, rel_heights  = c(1, 1.5, 0.5),rel_widths  = c(0.1, 2, 0.1))
plot_grid(p1,p2_1, rel_widths = c(16, 7), rel_heights  = c(9, 1), align = "none")

FIGURE 4 POLLINATOR COVERAGE

FIGURE 5? CLIFFHANGER OF NETWORK METRICS

@@

Geographic and taxonomic biases!

@@

Supplementary text 1

Habitat definitions:

1) **Ruderal vegetation**: Plants growing on highly disturbed sites such as road sides or mineral extraction sites.

2) **Agricultural margings**: Sides of crops that can include any type of vegetation from low growing plants to trees.

3) **Green urban areas**: Parks, private gardens or small pastures within an  urban setting. Botanical gardens are included in this category.

4) **Agricultural land**: Includes any type of crop and any type of vegetation growing within them.

5) **Forest/woodland understory**: Any plant community sampled under a wooded group of plants. The forest could be embedded in an agricultural setting or in a fully natural scenario. We have included here agro-forestry areas and open to dense forest. Note that we have excluded from this category forest that contains sclerophyllous vegetation.

6) **Semi-natural grassland**: Low growing plant community with relatively low disturbances but under low pressure such as seasonal mowing or extensive grazing.

7) **Pastures**: Any type of low growing plant community that is highly influenced by human disturbance. For instance, agriculture, mowing, moderate to high grazing or urban environments. Note that this category also includes old pastures with regrowth of woody vegetation.

8) **Sclerophyllous vegetation**: Any type of system with a dominant shrub community adapted to drought. Typical of the Mediterranean region. Note, that we have include in this category also woodlands (open coniferous forest) where the shrub community was the main focus of the study.

9) **Beaches, dunes, sands**: Plant communities growing on sandy soil.

10) **Riparian vegetation**: Plant communities growing on river margins.

10) **Natural grassslands**: Low growing plant communities with little or none human disturbance. Often located in high elevation areas within Europe.

12) **Moors and heathland**: Low growing woody vegetation characteristic from low fertile soils near the coast or in alpine areas.
